Constraining Black Hole Growth with High-z Quasar Observations

### 2022-08-05 ms.tex
version 0805; N_detect added; GLF+QLF plot; summary from k

For the two cases, the best-fit solutions consistently show a small values of $\delta < 0.01$.
%, which is sufficiently small and should be marginalized out. 
This suggests that in our model assumption, a nearly exponential BH growth pattern is favored. 
% In other words, on average the BH growth can be described as exponential, 
% under the premise that the gas supply is episodical. 
The typical duration of quasar activity is required to be $\tlife \simeq 29$ Myr for both the cases, 
which is $\sim 64\%$ of the $e$-folding time for an exponential growth.
This suggests that accreting seed BHs vary their growth speeds (i.e., the Eddington ratio) 
$\sim 30$ times on average, toward the cosmic time of $t_{\rm H} \gtrsim 900$ Myr at $z\simeq 6$.
The timescale of $\tlife$ also gives a lower bound of the quasar lifetimes of $t_{\rm Q}\sim 1-10$ Myr, 
which are estimated by the measurement of the physical extents of hydrogen Ly$\alpha$ proximity zones 
observed in the rest-frame UV spectra (e.g., Eilers+2018, Davies+ 2019).\red{KI: we need to figure out 
if their $t_Q$ is the quasar age or lifetime, or something else?}
More detailed comparison is discussed in \S\ref{sec:evol}.

@@

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{BHMF_rhoz.png}
\caption{
{\it Left panel}: BH mass functions at different redshifts of $6\leq z \leq 10$.
The solid lines denote modeled BHMF produced by the best-fit parameters 
and the shaded regions present the $1\sigma$ spread. 
{\it Right panel}: the redshift evolution of the cumulative mass density of BHs with $\Mbh \geq 10^7~\Msun$ in a comoving volume, 
evaluated by the integration of the BHMF shown in the left panel.
The evolutionary trend can be approximated as $\rho_\bullet (z) \propto 10^{k_M z}$, where $k_M\simeq -0.8$.
}
\label{fig:BHMF_rhoz}
\end{figure*}

\begin{table}
\renewcommand\thetable{1} %! fix indexing
\caption{$\rho_\bullet(z)$ Evolution Parameters}
\begin{center}
% \tablenum{1}
\begin{tabular}{l c r}
\hline
$M_{\rm min}$ & $\log \rho_{\bullet,0}$ & $k_{\rm M}$ ~~~ \\ 
\hline 
\hline
10$^7$  &  $-5.91\pm 0.28$  &  $-0.58 \pm 0.21$  \\
10$^8$  &  $-6.93\pm 0.47$  &  $-0.78 \pm 0.31$  \\
% 10$^9$  &  $-8.30_{-0.47}^{+0.47}$  & $-1.04_{-0.58}^{+0.54}$ \\
10$^9$  &  $-8.30\pm 0.47$  &  $-1.04 \pm 0.58$ \\
\hline 
\end{tabular}
\label{tab:MFz}
\end{center}
\end{table}

@@

In the left panel of Fig.~\ref{fig:BHMF_rhoz}, we show the BHMFs at five different redshifts of $z=6-10$.
For all the redshifts, the BHMFs can be characterized with a double power-law function, similar to lower-$z$ quasar populations.
From higher to lower redshifts, the number density of BHs heavier than $M_\bullet = 10^7~\Msun$ increases
and the high-mass tail of the distribution is extended owing to efficient growth of the most massive BH population.
%The number density of BHs with $\Mbh=10^7~\Msun$ emerging from high redshifts increase by a factor of $\sim 4$ per unit redshift.
In the right panel of Fig.~\ref{fig:BHMF_rhoz}, we also present the cumulative mass density of BHs with $\Mbh \geq M_{\rm min}$ in a comoving volume,
defined by the integration of the BHMF as
%
\begin{equation}
 \rho_\bullet(z)=\int_{M_{\rm min}}^{\infty} \Phi_{\Mbh} (z) \Mbh \D \log \Mbh,
\end{equation}
%
%as a function of redshift.
where we set the minimum mass to $M_{\rm min}=10^7$, $10^8$, and $10^9~\Msun$.
This result shows that the early BH assembly takes place rapidly and the redshift-dependence can be approximated by
%
\begin{equation}
\rho_\bullet(z)
%= \rho_{\bullet 0}\cdot e^{k_{\rm M}(z-6)}
\simeq \rho_{\bullet,0}~ 10^{k_{\rm M}(z-6)},
\end{equation}
%
where the fitted values of $\rho_{\bullet,0}$ and $k_{\rm M}$ are shown in Table.~\ref{tab:MFz}.
On the other hand, the stellar mass density of the quasar progenitor halos is calculated as
%
\begin{equation}
\rho_{\star}(z)
\simeq f_\star n_{\Mh} M_h~ 10^{k_{\rm h}(z-6)},
\end{equation}
%
where $f_\star(\equiv M_\star/\Mh)$ is the mass ratio of the galaxy stellar mass to the DM halo mass and
$n_{\Mh}$ is the number density of quasar host halos with $\Mh$ in a comoving volume at $z=6$; namely,
the value of $n_{\Mh}\Mh \simeq (6.2-99)\times 10^6~\Msun~{\rm Mpc}^{-3}$.
We here express the mass growth of the DM halo with a functional form of $\propto 10^{k_{\rm h} z}$,
which nicely reproduces the mass growth of DM halos
\citep[e.g.,][]{2002ApJ...568...52W,2008MNRAS.383..615N,2008MNRAS.388.1792N,2010MNRAS.406.2267F}
\footnote[3]{
In fact, this redshift dependence leads to a halo-mass growth rate of $\D \left(\ln \Mh \right) / \D t \propto(1+z)^{5/2}$,
which has been understood based on the extended Press-Schechter formalism and also derived by
a fit to merger trees from cosmological N-body simulations \citep{2013MNRAS.435..999D}.}.
% The redshift dependence yields the cosmic BH growth rate in the matter-dominated universe
% as $\dot{\rho}_\bullet \propto \rho_\bullet (1+z)^{5/2}$ or

@@

\subsection{Quasar luminosity function}

Next, we show the QLFs at different redshifts of $z=6-10$ taken from the BH growth model in the left panel of Fig.~\ref{fig:QLF_rhoz}.
%The model QLFs we propose give interesting prediction and will be further constrained by higher redshift quasar observations.
\red{KI: add more explanations about the QLFs. How about the detection limits of Euclid, Roman, and others?
Also, you could compare your results with Aaron Yung's results.}
In the right panel of Fig.~\ref{fig:QLF_rhoz}, we present the number density of luminous quasars with $\Muv <-26$ as a function of redshift.
The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$, where $k_{\rm L}\approx -0.97$.
A rapid decay of the quasar number density toward higher redshifts is found by previous studies \citep[e.g.,][]{2001AJ....122.2833F,2016ApJ...833..222J},
which show $k_{\rm L}= -0.47$ and $-0.72$ from the analysis of quasar samples at $z\simeq 3-5$ and $z\simeq 5-6$, respectively.
Recently, a steeper decline of luminous quasar number density toward higher redshifts is proposed by \citet{2019ApJ...884...30W},
suggesting $k_{\rm L}=-0.78$ at $6\lesssim z \lesssim 7$.
%a steeper decline ifts is suggested in recent studies of $z\gtrsim 6$ quasars,
%e.g. \citet{2019ApJ...884...30W} measure the spatial density of $z\sim 6.7$ quasars,
%and fit the parameter $k_{\rm L}=-0.78$ by connecting the $z\sim 6$ result from \citet{2016ApJ...833..222J}.
The rapid decline toward higher redshifts is nicely characterized by the treatment of episodic natures of BH accretion with a finite value of
$\tau ~(\simeq 20~{\rm Myr})$, in order to match the statistical properties of high-$z$ quasars.
We also note that the tendency would be explained by the rarity of massive quasar-host halos at higher redshifts,
non-constant radiative efficiencies that covert the BH growth rate into the luminosity, or some combination of these effects
\citep[e.g.,][]{2010ApJ...718..231S}.
%Studies with the assumption of the close correlation of DM halo mass with central BH mass, and a constant Eddington ratio 
%interprete this rapid decline by the rarity of massive halos toward higher redshifts \citep[e.g.,][]{2010ApJ...718..231S}, 
%while another entangling factor is the radiative efficiency in converting BH growth rate to luminosity. 
%In our work, we argue that the episodical BH accretion with bursts and quiescent phases is 
%important in matching the $z\sim 6$ quasar observations, 
%and this calls consideration of the more realistic BH-galaxy coevolution in understanding the observable AGN properties.

@@

\red{KI: still not sure what we discuss below... among the 7 BHs, is anyone consistent with Feige's BH?}
In \citet{2021ApJ...907L...1W}, they discover the currently known most distant quasar at $z=7.642$, 
tracing back with Eddington accretion, the central BH reaches the $10^{4-6}~\Msun$ seed mass range at $z=$ 30. 
However in our best-fit model, we observe that to trace back BH mass and understand their seeding scenarios, 
taking constant Eddington ratio derived from high-$z$ observation or assuming $\lambda=1$ are both unrealistic. 
Therefore we raise a caveat that under these assumptions the seed mass achieved may be unreliable. 
Instead we should take into account the episodical accretion nature of quasars, 
including both bursts of accretion and quiescent phases.
% This is supported strongly by our best model of a $\gtrsim 20$ Myr $\tlife$, which is intrinsically connected with 
% the observational active quasar episode.

@@

>>>>

For the two cases, the best-fit solutions consistently show a small values of $\delta < 0.01$.
%, which is sufficiently small and should be marginalized out. 
This suggests that in our model assumption, a nearly exponential BH growth pattern is favored. 
% In other words, on average the BH growth can be described as exponential, 
% under the premise that the gas supply is episodical. 
The typical duration of quasar activity is required to be $\tlife \simeq 29$ Myr for both the cases, 
which is $\sim 64\%$ of the $e$-folding time for an exponential growth.
This suggests that accreting seed BHs vary their growth speeds (i.e., the Eddington ratio) 
$\sim 30$ times on average, toward the cosmic time of $t_{\rm H} \gtrsim 900$ Myr at $z\simeq 6$.
The timescale of $\tlife$ also gives a lower bound of the quasar lifetimes of $t_{\rm Q}\sim 1-10$ Myr, 
which are estimated by the measurement of the physical extents of hydrogen Ly$\alpha$ proximity zones 
observed in the rest-frame UV spectra \citep[e.g.,][]{2018ApJ...867...30E,2019ApJ...884L..19D}.
% \red{KI: we need to figure out if their $t_Q$ is the quasar age or lifetime, or something else?}
More detailed comparison is discussed in \S\ref{sec:evol}.

@@

%%%%%%%
%    Fig. 
%%%%%%%
\begin{figure*}
\centering
\includegraphics[width=160mm]{BHMF_rhoz.png}
\caption{
{\it Left panel}: BH mass functions at different redshifts of $6\leq z \leq 10$.
The solid lines denote modeled BHMF produced by the best-fit parameters 
and the shaded regions present the $1\sigma$ spread. 
{\it Right panel}: the redshift evolution of the cumulative mass density of BHs with $\Mbh \geq 10^7~\Msun$ in a comoving volume, 
evaluated by the integration of the BHMF shown in the left panel.
The evolutionary trend can be approximated as $\rho_\bullet (z) \propto 10^{k_M z}$, where $k_M\simeq -0.68$.
}
\label{fig:BHMF_rhoz}
\end{figure*}

\begin{table}
\renewcommand\thetable{1} %! fix indexing
\caption{$\rho_\bullet(z)$ Evolution Parameters}
\begin{center}
% \tablenum{1}
\begin{tabular}{l c r}
\hline
$M_{\rm min}$ & $\log \rho_{\bullet,0}$ & $k_{\rm M}$ ~~~ \\ 
\hline 
\hline
10$^7$  &  $ 1.81\pm 0.28$  &  $-0.68 \pm 0.21$  \\
10$^8$  &  $ 1.54\pm 0.47$  &  $-0.84 \pm 0.31$  \\
% 10$^9$  &  $-8.30_{-0.47}^{+0.47}$  & $-1.04_{-0.58}^{+0.54}$ \\
10$^9$  &  $ 1.01\pm 0.47$  &  $-1.01 \pm 0.58$ \\
\hline 
\end{tabular}
\label{tab:MFz}
\end{center}
\end{table}

\begin{table*}
{ % group it, so that centering can work?
\centering
\renewcommand\thetable{2} %! fix indexing
\caption{Detection number of quasars estimated for future surveys}
% \tablenum{2}
\begin{tabular}{lcccccccccccc}
\hline Telescope & Survey area & Photo. depth & $N(z\sim 6)$ & $N(z\sim 7)$ & $N(z\sim 8)$ & $N(z\sim 9)$ & $N(z\sim10)$ \\
& (\rm{deg}$^2$) & (AB~mag) \\
\hline 
% 6758..6598057248175, 1514.3392258726712, 349.27228533671644, 85.15836783444871, 25.
Deep \it{LSST}   & 18000 & 27.5 & 73865 & 18470 &  4688 & 1237 & 389\\
Wide \it{RST}    &  2000 & 27   & 6758 &  1514 &  349 & 85 & 25  \\
Wide \it{Euclid} & 15000 & 24   & 6653  &  708 &   93 & 14 & 2  \\
\hline
\end{tabular}
\label{tab:N_detect}
}
\end{table*}

@@

In the left panel of Fig.~\ref{fig:BHMF_rhoz}, we show the BHMFs at five different redshifts of $z=6-10$.
For all the redshifts, the BHMFs can be characterized with a double power-law function, similar to lower-$z$ quasar populations.
From higher to lower redshifts, the number density of BHs heavier than $M_{\rm min} = 10^7~\Msun$ increases
and the high-mass tail of the distribution is extended owing to efficient growth of the most massive BH population.
%The number density of BHs with $\Mbh=10^7~\Msun$ emerging from high redshifts increase by a factor of $\sim 4$ per unit redshift.
In the right panel of Fig.~\ref{fig:BHMF_rhoz}, we also present the cumulative mass density of BHs with $\Mbh \geq M_{\rm min}$ in a comoving volume,
defined by the integration of the BHMF as
%
\begin{equation}
 \rho_\bullet(z)=\int_{M_{\rm min}}^{\infty} \Phi_{\Mbh} (z) \Mbh \D \log \Mbh.
\end{equation}
%
%as a function of redshift.
Varying the minimum mass as $M_{\rm min}=10^7$, $10^8$, and $10^9~\Msun$,
we find that the early BH assembly takes place rapidly and the redshift-dependence can be approximated by
%
\begin{equation}
\rho_\bullet(z)
%= \rho_{\bullet 0}\cdot e^{k_{\rm M}(z-6)}
\simeq \rho_{\bullet,0}~ 10^{k_{\rm M}(z-6)},
\end{equation}
%
where the fitted values of $\rho_{\bullet,0}$ and $k_{\rm M}$ are shown in Table.~\ref{tab:MFz}.
On the other hand, the stellar mass density of the quasar progenitor halos is calculated as
%
\begin{equation}
\rho_{\star}(z)
\simeq f_\star n_{\Mh} M_h~ 10^{k_{\rm h}(z-6)},
\end{equation}
%
where $f_\star(\equiv M_\star/\Mh)$ is the mass ratio of the galaxy stellar mass to the DM halo mass and
$n_{\Mh}$ is the number density of quasar host halos with $\Mh$ in a comoving volume at $z=6$; namely,
the value of $n_{\Mh}\Mh \simeq (6.2-99)\times 10^6~\Msun~{\rm Mpc}^{-3}$.
We here express the mass growth of the DM halo with a functional form of $\propto 10^{k_{\rm h} z}$,
which nicely reproduces the mass growth of DM halos
\citep[e.g.,][]{2002ApJ...568...52W,2008MNRAS.383..615N,2008MNRAS.388.1792N,2010MNRAS.406.2267F}
\footnote[3]{
In fact, this redshift dependence leads to a halo-mass growth rate of $\D \left(\ln \Mh \right) / \D t \propto(1+z)^{5/2}$,
which has been understood based on the extended Press-Schechter formalism and also derived by
a fit to merger trees from cosmological N-body simulations \citep{2013MNRAS.435..999D}.}.
% The redshift dependence yields the cosmic BH growth rate in the matter-dominated universe
% as $\dot{\rho}_\bullet \propto \rho_\bullet (1+z)^{5/2}$ or

@@

\subsection{Quasar luminosity function}
On the other hand, the statistics of BH masses together with the ERDF in their growth history can rebuild quasar luminosity functions across cosmic time,
which is interesting to be probed with future observations.
In Fig.~\ref{fig:LFs}, we show the QLF prediction by the best-fit model with 1-$\sigma$ scatter at redshifts $z=$ 7 to 10.
Considering the scarcity of faint quasars ($\Muv\gtrsim -20$) sampled in \citet{2014ApJ...786..104U},
we emphasize that the observed (Type I) QLF after the current obscuration prescription can be highly uncertain in the faint end,
which is to be improved by the future equipments.
% More thorough studies on the high-$z$ quasar obscuration by upcoming equipments will improve the understanding on this aspect.
We also produce the intrinsic (Type I and Type II) luminosity function without obscuration effects.
The QLF emgerging from high redshifts quickly evolves toward brighter luminosity 
with the number of quasars increases as BHs grow.

Thanks to numerous efforts in the high-$z$ galaxy observation field,
we overlay the galaxy UV luminosity function at each redshift,
with both binned data points and the fitting functions in Schechter and double power law (DPL) shape
\citep{2021AJ....162...47B,2022ApJS..259...20H,2020MNRAS.493.2059B,2022arXiv220712356D,2013MNRAS.432.2696M,2019ApJ...883...99S,
2022ApJ...929....1H,2018ApJ...867..150M,2022arXiv220801612H,2016ApJ...819..129O,2022arXiv220709434N}.
Compared to our QLF predictions, galaxies prevail in the faint end at all these redshifts,
with their LFs quickly declines toward the luminous end.%, where quasars outshine.
The large number of galaxies with $\Muv\gtrsim -23$ makes it prohibitive to probe rare quasars among the faint objects detected.
While with increasing luminosity, the extrapolation of galaxy LF curve with the Schechter fitting function drops quickly,
crossing the QLF at $\Muv$ at critical values of $\Muv\sim-23$, $-24$, and $-25$ at redshifts $z=7-8$, $9$, and $10-13$, respectively.
While for the galaxy LF fitted by DPL function,
the corresponding crossing point shifts to $\Muv\sim-26$, $-25$, and $\ll -30$.
Therefore the galaxy contamination effect on quasar observations still remains model-dependent. 
In the future, deep and wide-field surveys e.g.,
Deep {\it{LSST}} \citep{2017arXiv170801617R}, Wide {\it{RST}} \citep{2019arXiv190205569A}, and Wide {\it{Euclid}} \citep{2011arXiv1110.3193L}
will be crucial to construct the LF data for high-$z$ quasars and galaxies,
categorizing them by spectroscopic diagnostics.
We show the detection limit of these surveys at each redshift in Fig.~\ref{fig:LFs},
demonstrating their capability of optimizing high-$z$ galaxy and quasar observations.
The adopted survey parameters is shown in Table.~\ref{tab:N_detect}.
The depths of detection will be pushed down to $\Muv\lesssim -20$,
which is able to uncover the critical luminosities at which the numbers of galaxies and quasars are comparable.
The number of high-$z$ quasars are also predicted at each redshift (Table.~\ref{tab:N_detect}),
with the assumption of the survey volume with $\Delta z =1$ and 100\% completeness.
The large sample of objects at those high redshifts will shed light on
the early coevolution of galaxies and BHs in a statistically unbiased way.

% Next, we show the QLFs at different redshifts of $z=6-10$ taken from the BH growth model in the left panel of Fig.~\ref{fig:QLF_rhoz}.
% %The model QLFs we propose give interesting prediction and will be further constrained by higher redshift quasar observations.
% \red{KI: add more explanations about the QLFs. How about the detection limits of Euclid, Roman, and others?
% Also, you could compare your results with Aaron Yung's results.}
In Fig.~\ref{fig:QLF_rhoz}, we present the number density of luminous quasars with $\Muv <-26$ as a function of redshift.
The evolutionary trend can be fitted as $\propto 10^{k_{\rm L}z}$, where $k_{\rm L}\approx -0.97$.
A rapid decay of the quasar number density toward higher redshifts is found by previous studies \citep[e.g.,][]{2001AJ....122.2833F,2016ApJ...833..222J},
which show $k_{\rm L}= -0.47$ and $-0.72$ from the analysis of quasar samples at $z\simeq 3-5$ and $z\simeq 5-6$, respectively.
Recently, a steeper decline of luminous quasar number density toward higher redshifts is proposed by \citet{2019ApJ...884...30W},
suggesting $k_{\rm L}=-0.78$ at $6\lesssim z \lesssim 7$.
%a steeper decline ifts is suggested in recent studies of $z\gtrsim 6$ quasars,
%e.g. \citet{2019ApJ...884...30W} measure the spatial density of $z\sim 6.7$ quasars,
%and fit the parameter $k_{\rm L}=-0.78$ by connecting the $z\sim 6$ result from \citet{2016ApJ...833..222J}.
The rapid decline toward higher redshifts is nicely characterized by the treatment of episodic natures of BH accretion with a finite value of
$\tau ~(\simeq 20~{\rm Myr})$, in order to match the statistical properties of high-$z$ quasars.
We also note that the tendency would be explained by the rarity of massive quasar-host halos at higher redshifts,
non-constant radiative efficiencies that covert the BH growth rate into the luminosity, or some combination of these effects
\citep[e.g.,][]{2010ApJ...718..231S}.
%Studies with the assumption of the close correlation of DM halo mass with central BH mass, and a constant Eddington ratio 
%interprete this rapid decline by the rarity of massive halos toward higher redshifts \citep[e.g.,][]{2010ApJ...718..231S}, 
%while another entangling factor is the radiative efficiency in converting BH growth rate to luminosity. 
%In our work, we argue that the episodical BH accretion with bursts and quiescent phases is 
%important in matching the $z\sim 6$ quasar observations, 
%and this calls consideration of the more realistic BH-galaxy coevolution in understanding the observable AGN properties.

\begin{figure*}
\gridline{\fig{M0r8_f2linLF_spreadz7_KI.pdf}{0.45\textwidth}{}
          \fig{M0r8_f2linLF_spreadz8_KI.pdf}{0.45\textwidth}{}}
\gridline{\fig{M0r8_f2linLF_spreadz9_KI.pdf}{0.45\textwidth}{}
          \fig{M0r8_f2linLF_spreadz10_KI.pdf}{0.45\textwidth}{}}
\caption{QLF evolution at redshifts from $z=7$ to $z\gtrsim 10$.
In all panels the solid lines denote modeled QLF produced by the best-fit parameters and the shaded regions present the $1\sigma$ spread. 
The intrinsic QLF without obscuration effect is shown in the dashed lines,
deviating from the observed QLF mostly in the faint end.
The expected depths and volumes of future surveys with
Deep {\it{LSST}}, Wide {\it{RST}}, and Wide {\it{Euclid}} are overlaid with the blue thin lines,
indicating the detectability of quasars at these redshifts.
High-$z$ galaxy LF data points (grey) and fitting functions in the Schechter (dotted  magenta line) and DPL (dash-dotted  magenta line) shapes are shown.
With the extrapolated galaxy LFs in different shapes,
the galaxy contamination effect on quasar selection can be estimated.
\label{fig:LFs}}
\end{figure*}

@@

% \red{KI: still not sure what we discuss below... among the 7 BHs, is anyone consistent with Feige's BH?}
In \citet{2021ApJ...907L...1W}, they discover the currently known most distant quasar at $z=7.642$, 
tracing back with Eddington accretion, the central BH reaches the $10^{4-6}~\Msun$ seed mass range at $z=$ 30. 
However in our best-fit model, we observe that to trace back BH mass and understand their seeding scenarios, 
taking constant Eddington ratio derived from high-$z$ observation or assuming $\lambda=1$ are both unrealistic. 
Therefore we raise a caveat that under these assumptions the seed mass achieved may be unreliable. 
Instead we should take into account the episodical accretion nature of quasars, 
including both bursts of accretion and quiescent phases.
% This is supported strongly by our best model of a $\gtrsim 20$ Myr $\tlife$, which is intrinsically connected with 
% the observational active quasar episode.

@@

\section{Summary}
In this paper, we propose a theoretical model for the redshift-dependent QLF and BHMF at $z\gtrsim 6$,
applying the initial mass function of seed BHs.
We assume that the early BH population experiences multiple accretion bursts, in each of which the Eddington ratio
is assigned following a Schechter distribution function.
We conduct the MCMC fitting procedure used to optimize the BH growth parameters
so that the observed BHMF and QLF at $z\simeq 6$ are simultaneously reproduced.
Our best-fit model to reproduce the QLF and BHMF at $z\simeq 6$ yields the ERDF characterized with the two parameters of
$(\lambda_0, \alpha)=(0.89,0.12)$ and $(0.87,0.20)$ for the BH seeding fraction of $\fseed = 0.01$ and $0.1$, respectively.
The models suggests that several episodes of modest super-Eddington accretion occur and each accretion phase lasts $\simeq 20-30$ Myr.
For longer (and shorter) burst durations, the number of BHs at the high mass end is over(-under) produced.
Therefore, multiple accretion bursts with variable Eddington ratios enable the early BH population to grow and shine,
consistent with the observed distribution functions.
Using the best-fit model parameters, we construct the redshift-dependent QLF and BHMF at $6\leq z \leq 10$.
The two functions suggest a rapid decay of the number and mass density of massive BHs and luminous quasars in a cosmic volume
toward higher redshifts as $\propto 10^{-k_i z}$, where $k_{\rm M}\simeq -0.68$ for the BH mass and $k_{\rm L}=$ for the quasar number.
The predicted value of the decay slope $k_{\rm L}$ is consistent with that estimated by previous observations for $z\simeq 6-7$ quasars
but tends to be slightly steeper at higher redshifts.
\red{Add comparison to GLFs and expected detection numbers }\blue{
Comparing to galaxy LFs at redshifts from $z=7$ to $z\gtrsim 10$, the QLFs we predict is burried in the faint end at $\Muv \gtrsim -23$ by the huge galaxy population,
which raises the challenge of select quasars from the high-$z$ faint objects.
While in the luminous end, quasars account for a significant fraction of high-$z$ UV luminosity function,
we predict the critical luminosity at which galaxy and quasars make equal contribution,
depending on the fitting function form of galaxy LFs.}
We further explore individual BH evolutionary tracks starting from the BH seeds, applying the BH growth model
with the best-fit parameters reproducing their statistical properties.
For massive BHs that reach $\gtrsim 10^8~\Msun$ by $z\simeq 6$, the average duty cycle of accretion is as high as $\simeq 15~\%$.
Since the duty cycle is nearly twice that of the entire population, the BH samples observed in $z\simeq 6$ quasars are
biased toward a population that undergoes active accretion episodes.
Multiple accretion-burst treatment nicely produces the mass assembly history of individual high$-z$ luminous quasars,
unlike the case where one single value of the Eddington ratio is assigned.
We also find that the observed Eddington-ratio distribution function is skewed to a log-normal shape from the intrinsic Shechter function
owing to detection limits of quasar observations.
Those results will be unveiled by future deep and wide surveys with the JWST, LSST, RST, and Euclid.
